GPU Acceleration of Machine Learning-Aided Facial Recognition and Edge-Based Motion Detection with NVIDIA CUDA

### 2015-12-11 documents/paper/paper.tex
added python subsection to motion detection section

\subsection{OpenCV and Python}
While CUDA is an excelent language for maximizing performance, it could be infeasible due to inexperience with C, time constraints, or lack of an NVIDIA GPU. To address these constraints, we also implemented our algorithms in Python using OpenCV. Python was chosen because it is very easy for inexperienced programmers to use and OpenCV was chosen because it offers many common image processing algorithms in a variety of languages.

@@

\subsection{High Level Python Implementation}
Python is a widely used big-data programming language because of its extensive library support in such areas and its ease of use.

>>>>

\subsection{OpenCV and Python}
While CUDA is an excelent language for maximizing performance, it could be infeasible due to inexperience with C, time constraints, or lack of an NVIDIA GPU. To address these constraints, we also implemented our algorithms in Python using OpenCV. Python was chosen because it is very easy for inexperienced programmers to use and OpenCV was chosen because it offers many common image processing algorithms in a variety of languages. Unfortunately using OpenCV limits us to the library's implementation, does not currently support the use of GPU parallelization in Python. To take advantage of the GPU and parallelization in Python we would have to use C wrappers, which defeats the purpose of our implementation in Python.

@@

\subsection{High Level Python Implementation}
The Python implementation of Algorithm 3 is very straightforward and looks almost exactly like the pseudo-code, making it easy to implement even for those with minimal programming experience.
\begin{lstlisting}[
	caption=Python implementation of the motion area estimation image,
	label=python-motion-area-estimattion-implementation
]
def detect_motion(e1, e2):
    height, width, depth = np.shape(e1)
    d = difference(e1, e2)
    d_prime = np.zeros((M, N), np.uint8)
    for i in range(M):
        for j in range(N):
            x = 0
            for i_prime in range(height/M):
                for j_prime in range(width/N):
                    if d[i*height/M+i_prime, j*width/N+j_prime] != 0:
                        x += 1
            if M*N*x/(height*width*1.0) > T:
                d_prime[i, j] = 255
    return d_prime
\end{lstlisting}
